NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-08-10 ms_nihao_budget.tex
resolution test for cold/cool gas fraction

>>>>

{\bf Since the resolution is one key parameter in simulation, and one
can imagine that with increased resolution, higher densities can be 
achieved in the CGM, potential leading to more cooling and larger
cold/cool gas fraction,
the convergence of the baryonic fraction predicted by NIHAO suite
is worth to estimate. Fig.~\ref{fig:budget_res} shows cold and cool
gas (HI + HeI) fraction color coded by number of dark matter particles 
per halo. In the plot, the number of dark matter partilce per halo spans 
2 magnitudes and has no correlation with cold and cool gas fraction. 
Therefore, we can conclude the resolution of NIHAO suite is 
proper to study the fractional baryon content.}
